An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-22 EconGrowthSeminar.Rnw
Massive rearrangement of the seminar, including CI vs. parameter graphs.

\begin{frame}{Coordinates of Analysis} %----------------------------
  \begin{itemize}
    \item{Country/Economy: 9 \\US, UK, JP, CN, ZA, SA, IR, TZ, ZM}
    \item{Economic Growth Model: 4 \\SF, CD, CES, LINEX}
    \item{Type of Energy: 3 \\Q, X, U}
  \end{itemize}
  Simplification: 1 country (US), 1 type of energy (Q)
\end{frame}

\minorSeparator{Single-factor Models}

\begin{frame}{Single Factor} %----------------------------
  \begin{center}
    \sfEqn
    \vspace{\baselineskip}

@@

\minorSeparator{Cobb-Douglas (without Energy)} %----------------------------

@@

\begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
  \begin{center}
    \cdeEqn
  \end{center}
  \begin{itemize}
    \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits historical data}
    \item{Almost identical to Cobb-Douglas without energy}
    \item{Perform grid search over $\gamma$}
    \item{Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
    \item{Respect sum constraint: $\alpha + \beta + \gamma = 1$}
    \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$}
  \end{itemize}
\end{frame}

@@

@@

@@

>>>>

\begin{frame}{Coordinates of Analysis} %----------------------------
  \begin{itemize}
    \item{Country/Economy: 9 \\US, UK, JP, CN, ZA, SA, IR, TZ, ZM}
    \item{Economic Growth Model: 4 \\SF, CD, CES, LINEX}
    \item{Type of Energy: 3 \\Q, X, U}
  \end{itemize}
  Simplification: 1 type of energy (Q)
\end{frame}

\minorSeparator{Curve-fitting as Optimization}

\begin{frame}{Example: Single-factor Model} %----------------------------
  \begin{center}
    \sfEqn
    \vspace{\baselineskip}

@@

@@

\begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
  \begin{center}\cdeEqn\end{center}
  \begin{itemize}
    \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits historical data}
    \item{Almost identical to Cobb-Douglas without energy}
    \item{Perform grid search over $\gamma$}
    \item{Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
    \item{Respect sum constraint: $\alpha + \beta + \gamma = 1$}
    \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$}
  \end{itemize}
\end{frame}

@@

\begin{frame}{$CI_{\gamma}$ and $\gamma$ in Cobb-Douglas} %----------------------------
  \begin{center}
    \cdeEqn\\
    \includegraphics<1>[height=2.5in]{figure_other/CI-gamma-1.pdf}
    \includegraphics<2>[height=2.5in]{figure_other/CI-gamma-2.pdf}
    \includegraphics<3>[height=2.5in]{figure_other/CI-gamma-3.pdf}
    \includegraphics<4>[height=2.5in]{figure_other/CI-gamma-4.pdf}
  \end{center}
\end{frame}

\begin{frame}{CI and $\gamma$ in Cobb-Douglas} %----------------------------
  Graph here of CI vs. $\gamma$ where each country abbreviation is plotted.
\end{frame}

\begin{frame}{Implications from Cobb-Douglas} %----------------------------
  \begin{center}\cdeEqn\end{center}
  \vspace{\baselineskip}

  \begin{itemize}
    \item{Energy parameter ($\gamma$) is either}
      \begin{itemize}
        \item{Small (US, JP, CN, SA, IR)}
        \item{Large CI (ZA, TZ, ZM)}
        \item{Exception: UK}
      \end{itemize}
    \vspace{\baselineskip}

    \pause
    \item{Direct energy input to economy ($q$)is unimportant as a Cobb-Douglas predictor of economic output ($y$)}
  \end{itemize}
\end{frame}

@@

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
  \begin{center}
    \cdeEqn\\
    \includegraphics<1>[height=2.5in]{figure_other/CI-delta-1.pdf}
    \includegraphics<2>[height=2.5in]{figure_other/CI-delta-2.pdf}
    \includegraphics<3>[height=2.5in]{figure_other/CI-delta-3.pdf}
    \includegraphics<4>[height=2.5in]{figure_other/CI-delta-4.pdf}
  \end{center}
\end{frame}

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
  Graph here of $CI_{\delta}$ vs. $\delta$ where each country abbreviation is plotted.
\end{frame}

\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
  \begin{center}
    \cdeEqn\\
    \includegraphics<1>[height=2.5in]{figure_other/CI-sigma-1.pdf}
    \includegraphics<2>[height=2.5in]{figure_other/CI-sigma-2.pdf}
    \includegraphics<3>[height=2.5in]{figure_other/CI-sigma-3.pdf}
    \includegraphics<4>[height=2.5in]{figure_other/CI-sigma-4.pdf}
  \end{center}
\end{frame}

\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
  Graph here of $CI_{\sigma}$ vs. $\sigma$ where each country abbreviation is plotted.
\end{frame}

\begin{frame}{Implications from CES} %----------------------------
  \begin{center}\cesEqn\end{center}
  \vspace{\baselineskip}

  \begin{itemize}
    \item{kl and e are complements, sigma small where it is distinguishable.}
    \item{Direct energy input to economy ($q$)is unimportant as a CES predictor of economic output ($y$), because delta is close to 1.0}
  \end{itemize}
\end{frame}

@@

\minorSeparator{Single-factor Model}

\minorSeparator{Cobb-Douglas Model}
